\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xurl}
\title{Protocol Entry 006: Generator 3 Primary Memory Confirmation Closure}
\author{BH Stability Vector Space Protocol Record}
\date{2026-07-21}
\begin{document}
\maketitle

\section*{Question}
Does a strictly causal self-history feature improve next-step $\lambda_{\rm bh}$
prediction beyond the frozen current-state and cadence baseline under a
selection-aware, within-track null?

\section*{Frozen design}
The baseline was $[\lambda_t,\Delta u_{t\rightarrow t+1}]$.  The candidate
grid was $\tau/T\in\{0.02,0.05,0.10,0.20\}$.  Memory was recomputed after
within-track-and-split permutation and kernel selection was repeated inside
every null replicate.  The confirmation used 2,000 null replicates and the
pre-frozen 300,000-row, 400-track sample.

\section*{Result}
\begin{center}
\begin{tabular}{lr}
\toprule
Quantity & Value \\
\midrule
Observed fractional RMSE improvement & 0.042627 \\
Null mean fractional improvement & 0.026412 \\
Null-adjusted order excess & 0.016215 \\
Null 95th percentile & 0.027086 \\
Exceedances & 0/2,000 \\
Plus-one one-sided $p$ & 0.0004998 \\
\bottomrule
\end{tabular}
\end{center}

The frozen confirmation passed.  The null-adjusted excess is approximately
1.62\%, above the declared 1\% practical floor.  Most of the raw improvement
remains null-preserved denoising and is not labeled memory.

\section*{Adjudication}
The authorized statement is: \emph{a small order-dependent self-history
predictive gain exists in the frozen TNG $\lambda$-track primary design beyond
the current state and cadence baseline}.  This closes the pre-registered
existence test.  No further permutations of the same design are authorized.

The result does not confirm structure beyond AR(3), identify a physical
timescale, establish independent H/S axes, establish host regulation, or admit
HRSM M.  Post-hoc AR(3) diagnostics remain separate and show scale-fragile,
short-scale order dependence with unresolved fixed-row depth.

\section*{Provenance}
Raw confirmation SHA-256: \nolinkurl{f3098426b7181802aa7ce9c08ab6411a2ed4d0a8dfb3e37148f30f246cc00c51}\\
Freeze manifest SHA-256: \nolinkurl{dfbba783a75e02da206ed2c1dc42bf39a1612738fa5dc3c0720e228795901776}

\end{document}
