\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs,longtable,array}
\usepackage[hidelinks]{hyperref}
\begin{document}
\section*{Logbook Entry 001: Protocol-Aware Black-Hole Claim Audit}
\textbf{Audit ID:} BH-PROTOCOL-AUDIT-001\\
\textbf{Protocol:} HRSM executable proxy admission v6\\
\textbf{Manifest SHA-256:} \texttt{f45c3679f4cb7fa16467b5a1990d81f4e79d2a95b0f6d759eece3e51b51ce699}
\subsection*{Purpose}
This entry adjudicates manuscript-facing claims before recoverability or memory coordinates are activated. It inventories frozen evidence, records numerical and construction caps, and prevents unsupported claims from entering the next manuscript revision.
\subsection*{Claim adjudication}
\small\begin{longtable}{p{1.5cm}p{3.5cm}p{9.2cm}}\toprule Claim & Verdict & Allowed headline \\\midrule\endhead
BH-C01 & allowed\_bounded & A reduced black-hole projection is operational in the tested simulation and survey branches. \\
BH-C02 & unresolved\_axis\_identity & Specific accretion rate is used provisionally as a forcing or throughput coordinate. \\
BH-C03 & audit\_required & S is an equilibrium-distance coordinate only where code, configuration, and equation use a concordant residual construction. \\
BH-C04 & blocked\_pending\_dimensionality & The Tier 1 composite is exploratory until redundancy and noise-matched effective dimensionality are audited. \\
BH-C05 & allowed\_bounded & In the frozen TNG Tier 1 branch, residence-based ripeness has a negative dispersion slope under the declared estimators, subject to provenance, effective-unit, and construction-null caps. \\
BH-C06 & rejected\_negative\_result & The ordinary-variance median-potential trend is tail dominated and fails robust re-estimation. \\
BH-C07 & allowed\_bounded & The GAMA D4000-offset branch is a directional, three-bin, resolution-limited observational analogue. \\
BH-C08 & numeric\_quarantine & The GAMA sigma-star construction is numerically quarantined pending clean reconstruction and target-side independence checks. \\
BH-C09 & rejected\_negative\_result & MaNGA demonstrates survey-scale portability but refuses a universal compression law. \\
BH-C10 & exploratory & The score is an exploratory contextual ranking whose component and rank stability can be audited. \\
BH-C11 & interpretive\_only & Extreme settlement outliers are candidates for independent merger and host-disturbance validation. \\
BH-C12 & forbidden\_not\_attempted & Memory remains unactivated until a frozen generator ladder survives admitted finite augmentations and time-order nulls. \\
BH-C13 & forbidden\_not\_attempted & Recoverability remains unactivated until an information-time-valid R predicts an independent later recovery event. \\
BH-C14 & forbidden\_not\_attempted & The current evidence supports at most a reduced Tier 1 projection while R and M remain future tests. \\
\bottomrule\end{longtable}\normalsize
\subsection*{Axis status}
\begin{tabular}{lll}\toprule Axis & Candidate files & Verdict \\\midrule
H & 64 & identity\_unresolved \\
R & 2 & candidate\_only \\
S & 162 & formula\_concordance\_required \\
M & 2 & candidate\_only \\
\bottomrule\end{tabular}
\subsection*{Outcome}
allowed\_bounded: 3; audit\_required: 1; blocked\_pending\_dimensionality: 1; exploratory: 1; forbidden\_not\_attempted: 3; interpretive\_only: 1; numeric\_quarantine: 1; rejected\_negative\_result: 2; unresolved\_axis\_identity: 1.\\
Numeric quarantine flags requiring review: 65. 
The current branch remains a reduced Tier 1 projection. Recoverability and memory are not activated by this audit. The next stage may begin only after the configuration and manifest hashes are frozen and the blocked formula, provenance, effective-unit, and numerical items are resolved or explicitly carried as caps.
\end{document}
